List of publications

### 2025-03-13 report/index.qmd
index correction

```{r}
#| results: asis
#| echo: false
list_files <- list.files(pattern = "yml$", path = dirname(params$file), full.names = TRUE)
for (f in list_files) {
    data <- yaml::read_yaml(f)
    cat(sprintf("\n\n- [%s](%s.html) (%i series)",
        data$datasetname,
        basename(tools::file_path_sans_ext(f)),
        length(data$series))
    )
}
```

>>>>

```{r}
#| results: asis
#| echo: false
list_files <- list.files(pattern = "yml$", path = dirname(params$file), full.names = TRUE)
for (f in list_files) {
    data <- yaml::read_yaml(f)
    cat(sprintf("\n\n- [%s](%s.html) (%i series)",
        data$datasetname,
        data$dataset,
        length(data$series))
    )
}
```
